\documentclass[]{deedy-resume-openfont}

\begin{document}

\namesection{Kristian}{Sakarisson}{ \urlstyle{same}\url{https://sakarisson.com} \\
\href{mailto:kristian@sakarisson.com}{kristian@sakarisson.com} | +358 50 51 31 743
}

\href{https://www.linkedin.com/in/kristiansakarisson/}{linkedin.com/in/kristiansakarisson/}

\section{Experience}

\runsubsection{Wolt}
\descript{| Engineering Team Lead, Adtech Team }
\location{Aug 2022 - Present | Helsinki, FI}
\begin{tightemize}
\item As the engineering team lead of the AdTech team at Wolt, I am responsible for leading a team of engineers in the development and maintenance of the advertising technology platforms that power Wolt's advertising business.
\item My main focus is on creating a positive and inclusive work environment where team members feel safe and supported, and are able to do their best work.
\item I am also leading the technical integration towards a shared advertising platform between Wolt and DoorDash, working closely with our partners to ensure a smooth and successful integration.
\item I work closely with product managers, designers, and other stakeholders to define and prioritize the team's roadmap and ensure that we are aligned with the broader goals of the company.
\item I also support the professional development of the team members by providing guidance, mentorship, and opportunities for learning and growth.
\end{tightemize}

\sectionsep

\runsubsection{Wolt}
\descript{| Web Developer, Support Group }
\location{Oct 2021 - Aug 2022 | Helsinki, FI}
\begin{tightemize}
\item Contributed to a data-driven team that focused on improving the efficiency of the support department.
\item Worked closely with my team to analyze data and use machine learning techniques to identify opportunities for improvement and make data-driven decisions.
\item Developed and maintained web-based tools and applications that were used by the support team.
\end{tightemize}

\runsubsection{Wolt}
\descript{| Front-End Competence Lead }
\location{Nov 2020 - Oct 2021 | Helsinki, FI}
\begin{tightemize}
\item At Wolt, frontend is our biggest export. Whether it's our internal admin tools, our main customer-facing website, our open-source projects, our Node.js backends or our cross-platform mobile applications, frontend technology is part of the daily lives of dozens of engineers at Wolt.

\item As frontend competence lead, my role was to facilitate knowledge sharing, documentation, mentorship, and all those frontend things that didn't quite fit into any specific team's agenda.
\end{tightemize}
\sectionsep

\runsubsection{Wolt}
\descript{| React Native Developer, Courier Group }
\location{Oct 2018 - Oct 2021 | Helsinki, FI}
\begin{tightemize}
\item Developed and maintained a complex React Native codebase that powers the Wolt Partner app, used by tens of thousands of courier partners to manage their daily tasks and interactions with our platform
\item We put a high effort at keeping the user experience great and in my opinion succeeded in doing so. Our Wolt Partner app has consistently had similar App Store and Google Play ratings as our main customer app, which is a pretty high bar.
\end{tightemize}
\sectionsep

\runsubsection{Druid.fi}
\descript{| Front-End Developer }
\location{Jan 2018 - Oct 2018 | Helsinki, FI}
\begin{tightemize}
\item Implemented and optimized a progressive web app (PWA) using React, Redux, and Webpack, resulting in improved performance, offline support, and user engagement.
\item Developed and maintained a suite of web-based applications and services, using a combination of React, Drupal, and Node.js.
\item Worked closely with customers to define requirements, design solutions, and deliver high-quality software on time and within budget.
\item Collaborated with other developers, designers, and stakeholders to ensure that the software met the needs of the business and the users.
\end{tightemize}
\sectionsep

\runsubsection{Munin}
\descript{| Full-Stack Developer }
\location{Jun 2016 – Dec 2017 | Tórshavn, FO}
\begin{tightemize}
\item Developed and maintained a suite of web-based applications and services, using a combination of Python, JavaScript, and MySQL.
\item Implemented and managed a secure and reliable network infrastructure, including servers, switches, and firewalls.
\item Worked closely with customers to define requirements, design solutions, and deliver high-quality software on time and within budget.
\end{tightemize}
\sectionsep

\runsubsection{Eysturskúlin}
\descript{| Programming Teacher}
\location{Jan 2016 – Dec 2016 | Tórshavn, FO}
\begin{tightemize}
\item Developed and taught a curriculum for high school students, covering the fundamentals of programming, using languages such as Python, JavaScript, and Scratch.
\item Created and led hands-on activities and projects that helped students learn and apply programming concepts, such as variables, loops, and functions.
\item Assessed and evaluated student progress, providing feedback and support to help them improve and succeed.
\end{tightemize}
\sectionsep

\runsubsection{Tórshavn Municipality}
\descript{| IT Supporter}
\location{May 2013 – Dec 2014 | Tórshavn, FO}
\begin{tightemize}
\item Managed and maintained the hardware and software infrastructure of the municipality.
\item Implemented and administered Active Directory.
\item Provided technical support and assistance to thousands of users.
\end{tightemize}
\sectionsep

\section{Education}
\runsubsection{University of the Faroe Islands}
\descript{| BSc in Software Engineering}
\sectionsep

\section{Languages}
\begin{minipage}[t]{.6\textwidth}
\subsection{Programming}
\location{Highly skilled:}
JavaScript \textbullet{} TypeScript \textbullet{} C\# \textbullet{} React.js \textbullet{} React Native \\
\location{Moderately skilled:}
ReScript \textbullet{} C++ \textbullet{} Python \textbullet{} PHP \textbullet{} Java \textbullet{} MongoDB \textbullet{} GraphQL \textbullet{} Continuous Integration \\
\location{Familiar:}
Amazon Web Services \textbullet{} Android \& iOS \textbullet{} MSSQL
\sectionsep
\end{minipage}
\hfill
\begin{minipage}[t]{.35\textwidth}
\subsection{Spoken \& Written}
\location{Native fluency:} English, Faroese, Danish\\
\location{Reading fluency:} Norwegian, Swedish, Icelandic\\
\location{Learning:} Finnish\\
\end{minipage}

\end{document}  \documentclass[]{article}
